\enlargethispage{\baselineskip}

\begin{thebibliography}{10}

\begin{scriptsize}

\bibitem{us-arxiv}
\newblock \url{https://arxiv.org/abs/1612.00531}.
%\bibitem{us-arxiv}
%C. Aslay, F. Bonchi, L. V.S. Lakshmanan, and, W. Lu.
%\newblock Revenue Maximization in Incentivized Social Advertising.
%\newblock In {\em {arXiv preprint arXiv:1612.00531} 2016}.

\bibitem{AbbassiBM15}
Z.~Abbassi, A.~Bhaskara, and V.~Misra.
\newblock Optimizing display advertising in online social networks.
\newblock In {\em {WWW} 2015}.

\bibitem{alon-etal-opt-budget-www2012}
N.~Alon, I.~Gamzu, and M.~Tennenholtz.
\newblock Optimizing budget allocation among channels and influencers.
\newblock In {\em WWW 2012}.
\bibitem{AslayLB0L15}
{\c{C}}.~Aslay, W.~Lu, F.~Bonchi, A.~Goyal, and L.~V.~S. Lakshmanan.
\newblock Viral marketing meets social advertising: Ad allocation with minimum
  regret.
\newblock {\em {PVLDB}}, 8(7):822--833, 2015.

\bibitem{bakshy12}
E.~Bakshy, D.~Eckles, R.~Yan, and I.~Rosenn.
\newblock Social influence in social advertising: evidence from field
  experiments.
\newblock In {\em EC 2012}.

\bibitem{bakshy2011}
E.~Bakshy, J.~M. Hofman, W.~A. Mason, and D.~J. Watts.
\newblock Everyone's an influencer: quantifying influence on twitter.
\newblock In {\em WSDM 2011}.

\bibitem{AdHeat}
H.~Bao and E.~Y. Chang.
\newblock Adheat: An influence-based diffusion model for propagating hints to
  match ads.
\newblock In {\em WWW 2010}.

\bibitem{BarbieriBM12}
N.~Barbieri, F.~Bonchi, and G.~Manco.
\newblock Topic-aware social influence propagation models.
\newblock In {\em ICDM 2012}.

\bibitem{BharathiKS07}
S.~Bharathi, D.~Kempe, and M.~Salek.
\newblock Competitive influence maximization in social networks.
\newblock In {\em WINE 2007}.

\bibitem{borgs14}
C.~Borgs, M.~Brautbar, J.~T. Chayes, and B.~Lucier.
\newblock Maximizing social influence in nearly optimal time.
\newblock In {\em SODA 2014}.

\bibitem{CarnesNWZ07}
T.~Carnes, C.~Nagarajan, S.~M. Wild, and A.~van Zuylen.
\newblock Maximizing influence in a competitive social network: a follower's
  perspective.
\newblock In {\em ICEC 2007}.

\bibitem{chalermsook}
P.~Chalermsook, A.~D. Sarma, A.~Lall, and D.~Nanongkai.
\newblock Social network monetization via sponsored viral marketing.
\newblock In {\em SIGMETRICS 2015}.

\bibitem{ChenWW10}
W.~Chen, C.~Wang, and Y.~Wang.
\newblock Scalable influence maximization for prevalent viral marketing in
  large-scale social networks.
\newblock In {\em KDD 2010}.

\bibitem{cohen14}
E.~Cohen, D.~Delling, T.~Pajor, , and R.~F. Werneck.
\newblock Sketch-based influence maximization and computation: Scaling up with
  guarantees.
\newblock In {\em CIKM 2014}.

\bibitem{conforti1984submodular}
M.~Conforti and G.~Cornu{\'e}jols.
\newblock Submodular set functions, matroids and the greedy algorithm: tight
  worst-case bounds and some generalizations of the rado-edmonds theorem.
\newblock {\em Discrete applied mathematics}, 7(3):251--274, 1984.

\bibitem{dagum2000optimal}
P.~Dagum, R.~Karp, M.~Luby, and S.~Ross.
\newblock An optimal algorithm for monte carlo estimation.
\newblock {\em SIAM Journal on computing}, 29(5):1484--1496, 2000.

\bibitem{DemaineHMMRSZ14}
E.~D. Demaine, M.~Hajiaghayi, H.~Mahini, D.~L. Malec, S.~Raghavan, A.~Sawant,
  and M.~Zadimoghaddam.
\newblock How to influence people with partial incentives.
\newblock In {\em {WWW} 2014}.

\bibitem{devanur12}
N.~R. Devanur, B.~Sivan, and Y.~Azar.
\newblock Asymptotically optimal algorithm for stochastic adwords.
\newblock In {\em EC 2012}.

\bibitem{feldman10}
J.~Feldman, M.~Henzinger, N.~Korula, V.~S. Mirrokni, and C.~Stein.
\newblock Online stochastic packing applied to display ad allocation.
\newblock In {\em ESA 2010}.

\bibitem{feldman09}
J.~Feldman, N.~Korula, V.~S. Mirrokni, S.~Muthukrishnan, and M.~P{\'{a}}l.
\newblock Online ad assignment with free disposal.
\newblock In {\em WINE 2009}.

\bibitem{goel08}
G.~Goel and A.~Mehta.
\newblock Online budgeted matching in random input models with applications to
  adwords.
\newblock In {\em SODA 2008}.

\bibitem{iyer2015submodularthesis}
R.~Iyer.
\newblock {\em Submodular Optimization and Machine Learning: Theoretical
  Results, Unifying and Scalable Algorithms, and Applications}.
\newblock PhD thesis, Univ. of Washington, 2015.

\bibitem{iyer2013submodular}
R.~K. Iyer and J.~A. Bilmes.
\newblock Submodular optimization with submodular cover and submodular knapsack
  constraints.
\newblock In {\em NIPS 2013}.

\bibitem{kempe03}
D.~Kempe, J.~M. Kleinberg, and {\'E}.~Tardos.
\newblock Maximizing the spread of influence through a social network.
\newblock In {\em KDD 2003}.

\bibitem{korte78}
B.~Korte and D.~Hausmann
\newblock An analysis of the greedy heuristic for independence systems.
\newblock In {\em Annals of Discrete Mathematics 1978}.

\bibitem{LeskovecKDD07}
J.~Leskovec, A.~Krause, C.~Guestrin, C.~Faloutsos, J.~M. VanBriesen, and N.~S.
  Glance.
\newblock Cost-effective outbreak detection in networks.
\newblock In {\em KDD 2007}.

\bibitem{lu2013bang}
W.~Lu, F.~Bonchi, A.~Goyal, and L.~V. Lakshmanan.
\newblock The bang for the buck: fair competitive viral marketing from the host
  perspective.
\newblock In {\em KDD 2013}.

\enlargethispage{\baselineskip}

\bibitem{mehta13}
A.~Mehta.
\newblock Online matching and ad allocation.
\newblock {\em Foundations and Trends in Theoretical Computer Science},
  8(4):265--368, 2013.

\bibitem{adwords}
A.~Mehta, A.~Saberi, U.~V. Vazirani, and V.~V. Vazirani.
\newblock Adwords and generalized online matching.
\newblock {\em J. {ACM}}, 54(5), 2007.

\bibitem{mirrokni12}
V.~S. Mirrokni, S.~O. Gharan, and M.~Zadimoghaddam.
\newblock Simultaneous approximations for adversarial and stochastic online
  budgeted allocation.
\newblock In {\em SODA 2012}.

\bibitem{nguyen2013budgeted}
H.~Nguyen and R.~Zheng.
\newblock On budgeted influence maximization in social networks.
\newblock {\em IEEE Journal on Selected Areas in Communications},
  31(6):1084--1094, 2013.

\bibitem{NguyenTD16}
H.~T. Nguyen, M.~T. Thai, and T.~N. Dinh.
\newblock Stop-and-stare: Optimal sampling algorithms for viral marketing in
  billion-scale networks.
\newblock In {\em SIGMOD 2016}.

\bibitem{tang2015influence}
Y.~Tang, Y.~Shi, and X.~Xiao.
\newblock Influence maximization in near-linear time: A martingale approach.
\newblock In {\em SIGMOD 2015}.

\bibitem{tang14}
Y.~Tang, X.~Xiao, and Y.~Shi.
\newblock Influence maximization: Near-optimal time complexity meets practical
  efficiency.
\newblock {\em SIGMOD 2014}.

\bibitem{tucker12}
C.~Tucker.
\newblock Social advertising.
\newblock {\em Available at SSRN 1975897}, 2012.

\bibitem{wang2011learning}
C.~Wang, R.~Raina, D.~Fong, D.~Zhou, J.~Han, and G.~Badros.
\newblock Learning relevance from heterogeneous social network and its
  application in online targeting.
\newblock In {\em SIGIR 2011}.

\bibitem{tang18}
Y.~Tang, X.~Tang, X.~Xiao, and Y.~Junsong.
\newblock Online processing algorithms for influence maximization.
\newblock {\em SIGMOD 2018}.


\end{scriptsize}

\end{thebibliography}
